### 2019-10-07 thesis/txt/3-data-set.tex
cleaned writing doc

\section{Collection Process}
For our inital data collection \emdash to get an impression of build logs from various projects and languages \emdash we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
our impression?
\todo{image!}

@@

>>>>

\section{Collection Process}
For our inital data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
our impression?
\todo{image!}

@@

    \paragraph{Description}
    learning steps combining keywords -> similar to how devs would learn from reading those models
